Untitled

### 2022-11-14 data/forward.Rmd
forward2

```{r}

@@

```{r cars}
summary(lm(formula = pov ~ hlth,data = countries1))
summary(lm(formula = pov ~ fdi,data = countries1))
summary(lm(formula = pov ~ reg,data = countries1))
summary(lm(formula = pov ~ mil,data = countries1))
summary(lm(formula = pov ~ lbr.part,data = countries1))
summary(lm(formula = pov ~ unemp,data = countries1))
summary(lm(formula = pov ~ trade,data = countries1))
summary(lm(formula = pov ~ pop.gwth.total,data = countries1))
summary(lm(formula = pov ~ pop.gwth.rural,data = countries1))
summary(lm(formula = pov ~ pop.gwth.urban,data = countries1))
summary(lm(formula = pov ~ gcf,data = countries1))
summary(lm(formula = pov ~ gdp.dflt,data = countries1))
summary(lm(formula = pov ~ trade,data = countries1))
```
```{r}
summary(lm(formula = pov ~ hlth+reg,data = countries1))
summary(lm(formula = pov ~ fdi+reg,data = countries1))
summary(lm(formula = pov ~ mil+reg,data = countries1))
summary(lm(formula = pov ~ lbr.part+reg,data = countries1))
summary(lm(formula = pov ~ unemp+reg,data = countries1))
summary(lm(formula = pov ~ trade+reg,data = countries1))
summary(lm(formula = pov ~ pop.gwth.total+reg,data = countries1))
summary(lm(formula = pov ~ pop.gwth.rural+reg,data = countries1))
summary(lm(formula = pov ~ pop.gwth.urban+reg,data = countries1))
summary(lm(formula = pov ~ gcf+reg,data = countries1))
summary(lm(formula = pov ~ gdp.dflt+reg,data = countries1))
summary(lm(formula = pov ~ trade+reg,data = countries1))
summary(lm(formula = pov ~ income+reg,data = countries1))

```
```{r}
summary(lm(formula = pov ~ income+reg,data = countries1))
summary(lm(formula = pov ~ hlth+reg+income,data = countries1))
summary(lm(formula = pov ~ fdi+reg+income,data = countries1))
summary(lm(formula = pov ~ mil+reg+income,data = countries1))
summary(lm(formula = pov ~ lbr.part+reg+income,data = countries1))
summary(lm(formula = pov ~ unemp+reg+income,data = countries1))
summary(lm(formula = pov ~ trade+reg+income,data = countries1))
summary(lm(formula = pov ~ pop.gwth.total+reg+income,data = countries1))
summary(lm(formula = pov ~ pop.gwth.rural+reg+income,data = countries1))
summary(lm(formula = pov ~ pop.gwth.urban+reg+income,data = countries1))
summary(lm(formula = pov ~ gcf+reg+income,data = countries1))
summary(lm(formula = pov ~ gdp.dflt+reg+income,data = countries1))
summary(lm(formula = pov ~ trade+reg+income,data = countries1))
```
```{r}
summary(lm(formula = pov ~ mil + reg + income, data = countries1))

```
```{r}
summary(lm(formula = pov ~ pop.gwth.urban + reg + income + mil, data = countries1))
summary(lm(formula = pov ~ hlth+reg+income+mil+pop.gwth.urban,data = countries1))
summary(lm(formula = pov ~ fdi+reg+income+mil+pop.gwth.urban,data = countries1))
summary(lm(formula = pov ~ lbr.part+reg+income+mil+pop.gwth.urban,data = countries1))
summary(lm(formula = pov ~ unemp+reg+income+mil+pop.gwth.urban,data = countries1))
summary(lm(formula = pov ~ trade+reg+income+mil+pop.gwth.urban,data = countries1))
summary(lm(formula = pov ~ pop.gwth.total+reg+income+mil+pop.gwth.urban,data = countries1))
summary(lm(formula = pov ~ pop.gwth.rural+reg+income+mil+pop.gwth.urban,data = countries1))
summary(lm(formula = pov ~ gcf+reg+income+mil+pop.gwth.urban,data = countries1))
summary(lm(formula = pov ~ gdp.dflt+reg+income+mil+pop.gwth.urban,data = countries1))
summary(lm(formula = pov ~ trade+reg+income+mil+pop.gwth.urban,data = countries1))
```
```{r}
countries9 <- countries1 %>% 
  select(Age, TotalWorkingYears, NumCourses, YearsAtCurrCompany, MonthlyIncome)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

>>>>

```{r}
df_count<-read.csv("../data/countries1.csv")
head(df_count)

set.seed(10)
index <- sort(sample(x = nrow(df_count), size = nrow(df_count)*.8))
train <- df_count[index, ]
test <- df_count[-index, ]
str(test)
```

income has highest adjusted r-square value =0.6105
```{r cars}
summary(lm(formula = pov ~ income,data = train))
summary(lm(formula = pov ~ reg,data = train))
summary(lm(formula = pov ~ edu.total,data = train))
summary(lm(formula = pov ~ hlth,data = train))
summary(lm(formula = pov ~ mil,data = train))
summary(lm(formula = pov ~ fdi,data = train))
summary(lm(formula = pov ~ lbr.part,data = train))
summary(lm(formula = pov ~ unemp,data = train))
summary(lm(formula = pov ~ trade,data = train))
summary(lm(formula = pov ~ pop.gwth.total,data = train))
summary(lm(formula = pov ~ pop.gwth.rural,data = train))
summary(lm(formula = pov ~ pop.gwth.urban,data = train))
summary(lm(formula = pov ~ gdp.dflt,data = train))
summary(lm(formula = pov ~ gcf,data = train))
summary(lm(formula = pov ~ trade,data = train))
summary(lm(formula = pov ~ gdp.pc,data = train))
summary(lm(formula = pov ~ lfdi,data = train))
summary(lm(formula = pov ~ lgdp.dflt,data = train))
summary(lm(formula = pov ~ lgdp.pc,data = train))

@@

#reg+income adjusted r-square=0.7031
```{r}
summary(lm(formula = pov ~ reg+income,data = train))
summary(lm(formula = pov ~ edu.total+income,data = train))
summary(lm(formula = pov ~ hlth+income,data = train))
summary(lm(formula = pov ~ mil+income,data = train))
summary(lm(formula = pov ~ fdi+income,data = train))
summary(lm(formula = pov ~ lbr.part+income,data = train))
summary(lm(formula = pov ~ unemp+income,data = train))
summary(lm(formula = pov ~ trade+income,data = train))
summary(lm(formula = pov ~ pop.gwth.total+income,data = train))
summary(lm(formula = pov ~ pop.gwth.rural+income,data = train))
summary(lm(formula = pov ~ pop.gwth.urban+income,data = train))
summary(lm(formula = pov ~ gdp.dflt+income,data = train))
summary(lm(formula = pov ~ gcf+income,data = train))
summary(lm(formula = pov ~ trade+income,data = train))
summary(lm(formula = pov ~ gdp.pc+income,data = train))
summary(lm(formula = pov ~ lfdi+income,data = train))
summary(lm(formula = pov ~ lgdp.dflt+income,data = train))
summary(lm(formula = pov ~ lgdp.pc+income,data = train))

```
#lgdp.pc+income+reg r=0.7364
```{r}
summary(lm(formula = pov ~ edu.total+income +reg,data = train))
summary(lm(formula = pov ~ hlth+income+reg,data = train))
summary(lm(formula = pov ~ mil+income+reg,data = train))
summary(lm(formula = pov ~ fdi+income+reg,data = train))
summary(lm(formula = pov ~ lbr.part+income+reg,data = train))
summary(lm(formula = pov ~ unemp+income+reg,data = train))
summary(lm(formula = pov ~ trade+income+reg,data = train))
summary(lm(formula = pov ~ pop.gwth.total+income+reg,data = train))
summary(lm(formula = pov ~ pop.gwth.rural+income+reg,data = train))
summary(lm(formula = pov ~ pop.gwth.urban+income+reg,data = train))
summary(lm(formula = pov ~ gdp.dflt+income+reg,data = train))
summary(lm(formula = pov ~ gcf+income+reg,data = train))
summary(lm(formula = pov ~ trade+income+reg,data = train))
summary(lm(formula = pov ~ gdp.pc+income+reg,data = train))
summary(lm(formula = pov ~ lfdi+income+reg,data = train))
summary(lm(formula = pov ~ lgdp.dflt+income+reg,data = train))
summary(lm(formula = pov ~ lgdp.pc+income+reg,data = train))
```
gdp.pc+income+reg+lgdp.pc r=0.7599
```{r}
summary(lm(formula = pov ~ edu.total+income +reg+lgdp.pc,data = train))
summary(lm(formula = pov ~ hlth+income+reg+lgdp.pc ,data = train))
summary(lm(formula = pov ~ mil+income+reg+lgdp.pc ,data = train))#0.7424
summary(lm(formula = pov ~ fdi+income+reg+lgdp.pc ,data = train))
summary(lm(formula = pov ~ lbr.part+income+reg+lgdp.pc ,data = train))
summary(lm(formula = pov ~ unemp+income+reg+lgdp.pc ,data = train))
summary(lm(formula = pov ~ trade+income+reg+lgdp.pc,data = train))
summary(lm(formula = pov ~ pop.gwth.total+income+reg+lgdp.pc,data = train)) #0.7433
summary(lm(formula = pov ~ pop.gwth.rural+income+reg+lgdp.pc,data = train))
summary(lm(formula = pov ~ pop.gwth.urban+income+reg+lgdp.pc,data = train))
summary(lm(formula = pov ~ gdp.dflt+income+reg+lgdp.pc,data = train)) #0.7466
summary(lm(formula = pov ~ gcf+income+reg+lgdp.pc,data = train))
summary(lm(formula = pov ~ trade+income+reg+lgdp.pc,data = train))
summary(lm(formula = pov ~ gdp.pc+income+reg+lgdp.pc,data = train)) #0.7599
summary(lm(formula = pov ~ lfdi+income+reg+lgdp.pc,data = train))
summary(lm(formula = pov ~ lgdp.dflt+income+reg+lgdp.pc,data = train))

```
```{r}
summary(lm(formula = pov ~ edu.total+income +reg+lgdp.pc,data = train))
summary(lm(formula = pov ~ hlth+income+reg+lgdp.pc ,data = train))
summary(lm(formula = pov ~ mil+income+reg+lgdp.pc ,data = train))
summary(lm(formula = pov ~ fdi+income+reg+lgdp.pc ,data = train))
summary(lm(formula = pov ~ lbr.part+income+reg+lgdp.pc ,data = train))
summary(lm(formula = pov ~ unemp+income+reg+lgdp.pc ,data = train))
summary(lm(formula = pov ~ trade+income+reg+lgdp.pc,data = train))
summary(lm(formula = pov ~ pop.gwth.total+income+reg+lgdp.pc,data = train)) 
summary(lm(formula = pov ~ pop.gwth.rural+income+reg+lgdp.pc,data = train))
summary(lm(formula = pov ~ pop.gwth.urban+income+reg+lgdp.pc,data = train))
summary(lm(formula = pov ~ gdp.dflt+income+reg+lgdp.pc,data = train)) 
summary(lm(formula = pov ~ gcf+income+reg+lgdp.pc,data = train))
summary(lm(formula = pov ~ trade+income+reg+lgdp.pc,data = train))
summary(lm(formula = pov ~ lfdi+income+reg+lgdp.pc,data = train))
summary(lm(formula = pov ~ lgdp.dflt+income+reg+lgdp.pc,data = train))
#highest r-square=0.7466
```
```{r}
lm1<-(lm(formula = pov ~ gdp.pc+income+reg+lgdp.pc,data = train))
summary(lm1)
```
```{r}
eval.metrics.linreg <- function(actual, predicted) {
  residual <- actual - predicted
  mse <- mean(residual ^ 2)
  mae <- mean(abs(residual))
  rmse <-  sqrt(mse)
  mape <- mean(abs(residual / actual)) * 100

  data.frame(
    MSE = mse,
    MAE = mae,
    RMSE = rmse,
    MAPE = mape
  )
}
predicted<-predict(lm1,newdata=test)
actual<-test$pov
eval.metrics.linreg(actual,predicted)
actual
predicted
```
